Large-scale harmonic patterns clustering

### 2010-02-25 Paper/Paper.tex
algo added

\documentclass{article}
\usepackage{ismir2010,amsmath,cite}
\usepackage{graphicx}
\usepackage{url}

@@

% Three addresses
% --------------
\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}

@@

\subsection{Cowbell Dataset}

@@

@@

\section{Conclusion}
We are awesome. Here's how:
\begin{itemize}
\item large-scale
\item smarter shingles, based on beats and bars
\item clusters good for encoding
\item clusters good for something else?
\item free online API, code available
\end{itemize}

>>>>

\documentclass{article}
\usepackage{ismir2010,amsmath,cite}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm,algorithmic}

@@

% Three addresses
% --------------
\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
% what order do we use? Thierry, Ron, Dan? is Juan on?

@@

\subsection{Cowbell Dataset}
We have $3,720,091$ non zero bars, a bar usually contains
$4$ beats.

@@

\subsection{Codebook Learning}
We initialize the codebook by choosing $K$ random points from our dataset.

\begin{algorithm}
\caption{Pseudocode of Vector Quantization}
\label{alg:vq}
\begin{algorithmic}
\STATE$l$ learning rate
\STATE$\{P_n\}$ set of patches
\STATE$\{C_k\}$ codebook of $K$ codes
%\STATE $m \leftarrow b$
\REQUIRE $0 < l \leq 1$
\FOR{$nIters$}
\FOR{$p \in \{P_n\}$}
\STATE$c \leftarrow min_{c \in C_k} dist(p,c)$
\STATE$c \leftarrow c + (p - c) * l$
\ENDFOR
\ENDFOR
\RETURN $u$
\end{algorithmic}
\end{algorithm}

@@

\section{Conclusion}
We are awesome. Here's how:
\begin{itemize}
\item large-scale
\item smarter shingles, based on beats and bars
\item clusters good for encoding
\item clusters good for something else?
\item free online API, code available\footnote{code not released yet to preserve submission's anonymity}
\item we have lab t-shirts
\end{itemize}
